Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-02 WSSSPE3/report/wg_main_training.tex
Update wg_main_training.tex
- added third Workshop on related activities.

\subsubsection{Fit with related activities} Two existing venues for discussion
of related activities are identified:

@@

>>>>

\subsubsection{Fit with related activities} Three existing venues for discussion
of related activities are identified:

@@

\item Workshop on Software Engineering for Sustainable Systems\footnote{\url{http://sustainabilitydesign.org/initiatives/se4susy/}}
\katznote{fix URL and change to cite}
